String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-04 2023-1-19/figures/cactus_plot_automatark.tex
experiment done

\documentclass[11pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=automatark,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt] coordinates {(1,0.004)(44,0.1929655172413793)(131,0.619)(218,1.054)(305,1.489)(392,1.9436666666666667)(479,2.461)(566,2.983)(653,3.505)(740,4.027)(827,4.583517241379311)(914,5.192)(1001,5.801)(1088,6.410114942528736)(1175,7.067)(1262,7.763)(1349,8.460206896551725)(1436,9.213)(1523,9.996)(1610,10.779)(1697,11.58373563218391)(1784,12.45)(1871,13.32)(1958,14.19)(2045,15.101034482758621)(2132,16.058)(2219,17.015)(2306,17.972)(2393,18.96351724137931)(2480,20.007)(2567,21.051)(2654,22.095)(2741,23.170045977011494)(2828,24.3)(2915,25.431)(3002,26.564655172413794)(3089,27.758)(3176,28.976)(3263,30.194632183908045)(3350,31.466)(3437,32.771)(3524,34.076)(3611,35.40875862068965)(3698,36.799)(3785,38.19365517241379)(3872,39.648)(3959,41.127)(4046,42.64232183908046)(4133,44.208)(4220,45.8121724137931)(4307,47.46741379310345)(4394,49.182)(4481,50.93724137931035)(4568,52.758758620689655)(4655,54.645)(4742,56.59175862068965)(4829,58.61818390804598)(4916,60.734206896551726)(5003,62.95365517241379)(5090,65.28090804597701)(5177,67.70108045977013)(5264,70.23856321839081)(5351,72.88997701149425)(5438,75.67103448275863)(5525,78.58893103448275)(5612,81.6562183908046)(5699,84.874)(5786,88.2651724137931)(5873,91.82601149425287)(5960,95.5585172413793)(6047,99.47231034482758)(6134,103.54482758620689)(6221,107.8031724137931)(6308,112.31964367816093)(6395,117.07937931034482)(6482,122.072091954023)(6569,127.33118390804597)(6656,132.8960804597701)(6743,138.7530804597701)(6830,144.9270459770115)(6917,151.4784712643678)(7004,158.41937931034485)(7091,165.80327586206894)(7178,173.69822988505746)(7265,182.17563218390805)(7352,191.24119540229884)(7439,201.0427931034483)(7526,211.73466666666667)(7613,223.59497701149425)(7700,236.8307471264368)(7787,252.0250344827586)(7874,270.1710804597701)(7961,293.053816091954)(8048,322.6413333333333)(8135,362.7002988505747)(8222,425.82054022988507)(8309,535.5033103448276)(8396,770.6830344827586)(8478.5,1487.735076923077)(8519,2580.115)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt] coordinates {(1,1.001)(44.5,49.77588636363636)(132.5,153.98013636363635)(220.5,262.1894545454545)(308.5,372.31238636363634)(396.5,483.76913636363633)(484.5,596.3042386363636)(572.5,709.8801022727273)(660.5,824.4665795454546)(748.5,940.0296818181818)(836.5,1056.4871704545453)(924.5,1173.8087727272728)(1012.5,1291.9674659090908)(1100.5,1410.8886590909092)(1188.5,1530.5722159090908)(1276.5,1651.1055568181819)(1364.5,1772.5285454545453)(1452.5,1894.8319431818181)(1540.5,2018.1299886363636)(1628.5,2142.4604431818184)(1716.5,2267.7058636363636)(1804.5,2393.9053636363637)(1892.5,2521.1623863636364)(1980.5,2649.336715909091)(2068.5,2778.3925568181817)(2156.5,2908.361522727273)(2244.5,3039.2929886363636)(2332.5,3171.2455681818183)(2420.5,3304.1568181818184)(2508.5,3437.978727272727)(2596.5,3572.7547045454544)(2684.5,3708.3190795454548)(2772.5,3844.8086704545453)(2860.5,3982.276659090909)(2948.5,4120.705352272727)(3036.5,4260.052625)(3124.5,4400.310102272728)(3212.5,4541.485136363637)(3300.5,4683.616443181819)(3388.5,4826.598465909091)(3476.5,4970.501204545454)(3564.5,5115.386761363637)(3652.5,5261.080522727272)(3740.5,5407.658522727273)(3828.5,5555.073136363637)(3916.5,5703.36828409091)(4004.5,5852.564125)(4092.5,6002.664488636363)(4180.5,6153.749011363637)(4268.5,6305.792931818181)(4356.5,6458.7932045454545)(4444.5,6612.791284090909)(4532.5,6767.785272727272)(4620.5,6923.865602272727)(4708.5,7081.039670454546)(4796.5,7239.417079545454)(4884.5,7399.086931818181)(4972.5,7560.03825)(5060.5,7722.204431818182)(5148.5,7885.649727272727)(5236.5,8050.295590909091)(5324.5,8216.39771590909)(5412.5,8384.032886363637)(5500.5,8553.316522727273)(5588.5,8724.139943181819)(5676.5,8896.458170454545)(5764.5,9070.357636363637)(5852.5,9245.943272727274)(5940.5,9423.107818181817)(6028.5,9602.053295454545)(6116.5,9782.941011363637)(6204.5,9965.751875)(6292.5,10150.460022727273)(6380.5,10337.203965909091)(6468.5,10525.924090909091)(6556.5,10717.150215909092)(6644.5,10910.920056818182)(6732.5,11107.200715909092)(6820.5,11306.398920454545)(6908.5,11508.439136363637)(6996.5,11713.935943181817)(7084.5,11923.624)(7172.5,12136.768875)(7260.5,12353.715988636362)(7348.5,12574.161954545456)(7436.5,12798.799136363637)(7524.5,13029.105806818181)(7612.5,13264.319659090908)(7700.5,13505.580909090908)(7788.5,13753.832738636364)(7876.5,14009.777022727274)(7964.5,14275.649375)(8052.5,14554.259579545454)(8140.5,14849.837511363638)(8228.5,15168.880022727273)(8316.5,15522.201875)(8404.5,15935.410215909093)(8492.5,16507.840431818182)(8580.5,17813.824431818182)(8631,19480.083)(8639,19878.963)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt] coordinates {(1,0.966)(45,51.629651685393256)(134,158.67904494382023)(223,269.89732584269666)(312,383.6197528089888)(401,499.6783033707865)(490,617.7793258426966)(579,737.6599775280899)(668,858.9771348314606)(757,981.355786516854)(846,1104.57902247191)(935,1228.659370786517)(1024,1353.5784606741574)(1113,1479.340449438202)(1202,1605.8423483146069)(1291,1732.994393258427)(1380,1860.7982471910111)(1469,1989.2398764044942)(1558,2118.2535730337077)(1647,2247.769235955056)(1736,2377.8024382022472)(1825,2508.35204494382)(1914,2639.348359550562)(2003,2770.839404494382)(2092,2902.8377078651683)(2181,3035.319370786517)(2270,3168.2678876404493)(2359,3301.7290674157307)(2448,3435.6920898876406)(2537,3570.1292921348318)(2626,3705.1524606741573)(2715,3840.691617977528)(2804,3976.759415730337)(2893,4113.360764044944)(2982,4250.445494382023)(3071,4388.062044943821)(3160,4526.229382022472)(3249,4664.950314606742)(3338,4804.172505617978)(3427,4943.860483146068)(3516,5084.05806741573)(3605,5224.723202247191)(3694,5365.906865168539)(3783,5507.576955056179)(3872,5649.704640449439)(3961,5792.306471910112)(4050,5935.380764044944)(4139,6078.9809550561795)(4228,6223.057966292135)(4317,6367.639449438202)(4406,6512.755247191011)(4495,6658.350494382023)(4584,6804.486224719101)(4673,6951.171146067415)(4762,7098.355382022472)(4851,7246.019595505618)(4940,7394.190629213483)(5029,7542.908370786517)(5118,7692.217370786517)(5207,7842.0449101123595)(5296,7992.411258426966)(5385,8143.2914269662915)(5474,8294.690213483147)(5563,8446.689786516854)(5652,8599.329584269663)(5741,8752.537707865169)(5830,8906.401494382022)(5919,9060.95129213483)(6008,9216.186011235954)(6097,9372.039516853933)(6186,9528.586505617977)(6275,9685.89011235955)(6364,9843.871674157303)(6453,10002.450629213485)(6542,10161.815808988766)(6631,10321.953292134831)(6720,10482.887561797754)(6809,10644.69070786517)(6898,10807.32670786517)(6987,10970.82293258427)(7076,11135.298629213485)(7165,11300.878033707864)(7254,11467.537505617978)(7343,11635.502033707864)(7432,11804.723314606741)(7521,11975.318898876405)(7610,12147.362651685393)(7699,12320.866617977528)(7788,12495.943325842698)(7877,12672.84586516854)(7966,12851.813775280898)(8055,13033.299011235955)(8144,13217.471460674158)(8233,13405.040426966292)(8322,13597.334921348314)(8411,13797.202966292136)(8500,14006.997168539327)(8589,14242.676)(8663.5,14719.4016)(8695,15616.104)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt] coordinates {(1,0.011)(28,0.34405454545454545)(83,1.004)(138,1.664)(193,2.324)(248,2.984)(303,3.6490181818181817)(358,4.355)(413,5.07)(468,5.785)(523,6.5)(578,7.215)(633,7.93)(688,8.645)(743,9.36)(798,10.075)(853,10.79)(908,11.505)(963,12.22)(1018,12.935)(1073,13.65)(1128,14.365)(1183,15.08)(1238,15.795)(1293,16.51)(1348,17.234018181818183)(1403,17.999)(1458,18.769)(1513,19.541781818181818)(1568,20.355)(1623,21.217)(1678,22.11927272727273)(1733,23.054)(1788,24.01127272727273)(1843,25.001)(1898,25.992654545454545)(1953,27.022)(2008,28.067)(2063,29.112)(2118,30.1666)(2173,31.262)(2228,32.362)(2283,33.462)(2338,34.564781818181814)(2393,35.707)(2448,36.862)(2503,38.017)(2558,39.172)(2613,40.35205454545454)(2668,41.562)(2723,42.772)(2778,43.99618181818182)(2833,45.259)(2888,46.524)(2943,47.80865454545455)(2998,49.128)(3053,50.47210909090909)(3108,51.8482)(3163,53.26290909090909)(3218,54.7376)(3273,56.27590909090909)(3328,57.87347272727273)(3383,59.548418181818185)(3438,61.30281818181818)(3493,63.13972727272727)(3548,65.0678909090909)(3603,67.10025454545455)(3658,69.2492)(3713,71.49483636363637)(3768,73.84325454545454)(3823,76.31507272727272)(3878,78.93901818181818)(3933,81.7334909090909)(3988,84.68719999999999)(4043,87.8238)(4098,91.12774545454545)(4153,94.64658181818182)(4208,98.41867272727274)(4263,102.46365454545455)(4318,106.77592727272727)(4373,111.44936363636363)(4428,116.65296363636364)(4483,122.39274545454545)(4538,128.6556)(4593,135.70430909090908)(4648,143.72623636363636)(4703,152.72258181818182)(4758,162.99996363636362)(4813,175.10872727272726)(4868,189.50578181818182)(4923,208.60178181818182)(4978,241.16914545454546)(5033,301.7078909090909)(5088,407.2800363636364)(5143,527.1198909090908)(5198,654.8019272727272)(5253,840.1544181818182)(5308,1365.6359454545457)(5363,2537.6238)(5400.5,4036.3596000000002)(5412,4631.644)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt] coordinates {(1,0.012)(44,0.5610344827586207)(131,1.688)(218,2.819)(305,3.95)(392,5.081)(479,6.212)(566,7.343)(653,8.474)(740,9.605)(827,10.736)(914,11.867)(1001,13.03806896551724)(1088,14.256)(1175,15.474)(1262,16.692)(1349,17.91)(1436,19.128)(1523,20.360655172413793)(1610,21.658)(1697,22.963)(1784,24.28096551724138)(1871,25.664)(1958,27.056)(2045,28.463241379310343)(2132,29.935)(2219,31.414)(2306,32.8931724137931)(2393,34.421)(2480,35.987)(2567,37.553)(2654,39.13308045977011)(2741,40.778)(2828,42.431)(2915,44.084)(3002,45.78)(3089,47.52)(3176,49.26)(3263,51.02618390804598)(3350,52.851)(3437,54.678)(3524,56.54132183908046)(3611,58.455)(3698,60.38365517241379)(3785,62.377)(3872,64.40044827586208)(3959,66.485)(4046,68.61403448275863)(4133,70.79366666666667)(4220,73.036)(4307,75.34001149425288)(4394,77.72368965517242)(4481,80.208)(4568,82.774)(4655,85.4200459770115)(4742,88.19042528735632)(4829,91.09298850574713)(4916,94.14202298850574)(5003,97.34010344827585)(5090,100.71949425287357)(5177,104.2736551724138)(5264,108.0643908045977)(5351,112.12058620689655)(5438,116.49328735632184)(5525,121.25075862068965)(5612,126.37032183908046)(5699,131.87488505747126)(5786,137.83209195402299)(5873,144.3935747126437)(5960,151.6332528735632)(6047,159.56349425287357)(6134,168.32394252873564)(6221,178.00933333333333)(6308,188.61080459770116)(6395,200.22363218390805)(6482,213.0765632183908)(6569,227.277816091954)(6656,243.0501379310345)(6743,260.7920344827586)(6830,280.4905517241379)(6917,302.7097586206897)(7004,327.5999540229885)(7091,355.8960229885057)(7178,388.3605862068966)(7265,425.57027586206897)(7352,467.78589655172414)(7439,515.8811034482759)(7526,572.8783908045978)(7613,640.500264367816)(7700,721.5446551724137)(7787,819.6228965517241)(7874,943.8886896551724)(7961,1102.410471264368)(8048,1306.6646551724136)(8135,1592.898448275862)(8222,2000.9801264367816)(8309,2632.139011494253)(8396,3684.789195402299)(8483,5632.933747126437)(8528.5,7474.12825)(8532,7620.921)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt] coordinates {(1,0.004)(45,0.1892247191011236)(134,0.615)(223,1.06)(312,1.505)(401,1.95)(490,2.395)(579,2.84)(668,3.285)(757,3.73)(846,4.175)(935,4.62)(1024,5.071303370786517)(1113,5.588)(1202,6.122)(1291,6.656)(1380,7.209224719101123)(1469,7.827)(1558,8.45)(1647,9.073)(1736,9.696)(1825,10.319)(1914,10.942)(2003,11.565)(2092,12.188)(2181,12.834370786516855)(2270,13.543)(2359,14.255)(2448,14.967)(2537,15.679)(2626,16.391)(2715,17.103)(2804,17.815)(2893,18.527)(2982,19.239)(3071,19.951)(3160,20.663)(3249,21.381685393258426)(3338,22.166)(3427,22.967)(3516,23.768)(3605,24.569)(3694,25.37)(3783,26.171)(3872,26.972)(3961,27.773)(4050,28.574)(4139,29.375)(4228,30.181932584269664)(4317,31.054)(4406,31.944)(4495,32.834)(4584,33.724)(4673,34.614)(4762,35.504)(4851,36.394)(4940,37.29030337078652)(5029,38.252)(5118,39.231)(5207,40.21)(5296,41.189)(5385,42.1703595505618)(5474,43.212)(5563,44.28)(5652,45.348)(5741,46.41661797752809)(5830,47.539)(5919,48.696)(6008,49.853)(6097,51.045505617977526)(6186,52.291)(6275,53.542932584269664)(6364,54.86)(6453,56.19924719101124)(6542,57.602)(6631,59.045887640449436)(6720,60.55431460674157)(6809,62.11923595505618)(6898,63.772)(6987,65.50240449438202)(7076,67.33822471910112)(7165,69.29493258426966)(7254,71.38649438202248)(7343,73.63291011235955)(7432,76.06348314606741)(7521,78.76337078651686)(7610,81.7866179775281)(7699,85.20116853932583)(7788,89.14226966292135)(7877,93.84008988764046)(7966,99.66762921348314)(8055,106.92501123595505)(8144,116.53524719101124)(8233,130.10767415730336)(8322,150.67694382022472)(8411,185.7845842696629)(8500,252.37134831460673)(8589,453.2947752808989)(8655.5,1213.1201363636364)(8679,2048.545)};
\addlegendentry{Z3str3RE}

>>>>

\documentclass[11.5pt]{standalone}
\usepackage{color}
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.16}
\begin{document}
\definecolor{colourCVC5}{HTML}{25333D}
\definecolor{colourOstrichCEA}{HTML}{0065AB}
\definecolor{colourOstrich}{HTML}{8939AD}
\definecolor{colourZ3str3}{HTML}{007E7A}
\definecolor{colourZ3seq}{HTML}{CD3517}
\definecolor{colourZ3str3RE}{HTML}{318700}
\definecolor{colourZ3-Trau}{HTML}{80746D}
\resizebox{.95\textwidth}{!}{\pgfplotsset{scaled x ticks=false}\pgfplotsset{scaled y ticks=false}\begin{tikzpicture}\begin{axis}[title=automatark,xlabel=Solved instances,ylabel=Time (s),,legend columns=2,legend style={nodes={scale=0.5, transform shape}, fill=none,anchor=east,align=center },axis line style={draw=none}, xtick pos=left, ytick pos=left, ymajorgrids=true, legend style={draw=none},x post scale=2,y post scale=1]
\addplot[name path=pathCVC5 , colourCVC5, line width=1.5pt,dashed, dash pattern=on 2pt off 8pt] coordinates {(1,0.004)(44,0.1929655172413793)(131,0.619)(218,1.054)(305,1.489)(392,1.9436666666666667)(479,2.461)(566,2.983)(653,3.505)(740,4.027)(827,4.583517241379311)(914,5.192)(1001,5.801)(1088,6.410114942528736)(1175,7.067)(1262,7.763)(1349,8.460206896551725)(1436,9.213)(1523,9.996)(1610,10.779)(1697,11.58373563218391)(1784,12.45)(1871,13.32)(1958,14.19)(2045,15.101034482758621)(2132,16.058)(2219,17.015)(2306,17.972)(2393,18.96351724137931)(2480,20.007)(2567,21.051)(2654,22.095)(2741,23.170045977011494)(2828,24.3)(2915,25.431)(3002,26.564655172413794)(3089,27.758)(3176,28.976)(3263,30.194632183908045)(3350,31.466)(3437,32.771)(3524,34.076)(3611,35.40875862068965)(3698,36.799)(3785,38.19365517241379)(3872,39.648)(3959,41.127)(4046,42.64232183908046)(4133,44.208)(4220,45.8121724137931)(4307,47.46741379310345)(4394,49.182)(4481,50.93724137931035)(4568,52.758758620689655)(4655,54.645)(4742,56.59175862068965)(4829,58.61818390804598)(4916,60.734206896551726)(5003,62.95365517241379)(5090,65.28090804597701)(5177,67.70108045977013)(5264,70.23856321839081)(5351,72.88997701149425)(5438,75.67103448275863)(5525,78.58893103448275)(5612,81.6562183908046)(5699,84.874)(5786,88.2651724137931)(5873,91.82601149425287)(5960,95.5585172413793)(6047,99.47231034482758)(6134,103.54482758620689)(6221,107.8031724137931)(6308,112.31964367816093)(6395,117.07937931034482)(6482,122.072091954023)(6569,127.33118390804597)(6656,132.8960804597701)(6743,138.7530804597701)(6830,144.9270459770115)(6917,151.4784712643678)(7004,158.41937931034485)(7091,165.80327586206894)(7178,173.69822988505746)(7265,182.17563218390805)(7352,191.24119540229884)(7439,201.0427931034483)(7526,211.73466666666667)(7613,223.59497701149425)(7700,236.8307471264368)(7787,252.0250344827586)(7874,270.1710804597701)(7961,293.053816091954)(8048,322.6413333333333)(8135,362.7002988505747)(8222,425.82054022988507)(8309,535.5033103448276)(8396,770.6830344827586)(8478.5,1487.735076923077)(8519,2580.115)};
\addlegendentry{CVC5}

\addplot[name path=pathOstrichCEA , colourOstrichCEA, line width=1.5pt, solid] coordinates {(1,1.001)(44.5,49.77588636363636)(132.5,153.98013636363635)(220.5,262.1894545454545)(308.5,372.31238636363634)(396.5,483.76913636363633)(484.5,596.3042386363636)(572.5,709.8801022727273)(660.5,824.4665795454546)(748.5,940.0296818181818)(836.5,1056.4871704545453)(924.5,1173.8087727272728)(1012.5,1291.9674659090908)(1100.5,1410.8886590909092)(1188.5,1530.5722159090908)(1276.5,1651.1055568181819)(1364.5,1772.5285454545453)(1452.5,1894.8319431818181)(1540.5,2018.1299886363636)(1628.5,2142.4604431818184)(1716.5,2267.7058636363636)(1804.5,2393.9053636363637)(1892.5,2521.1623863636364)(1980.5,2649.336715909091)(2068.5,2778.3925568181817)(2156.5,2908.361522727273)(2244.5,3039.2929886363636)(2332.5,3171.2455681818183)(2420.5,3304.1568181818184)(2508.5,3437.978727272727)(2596.5,3572.7547045454544)(2684.5,3708.3190795454548)(2772.5,3844.8086704545453)(2860.5,3982.276659090909)(2948.5,4120.705352272727)(3036.5,4260.052625)(3124.5,4400.310102272728)(3212.5,4541.485136363637)(3300.5,4683.616443181819)(3388.5,4826.598465909091)(3476.5,4970.501204545454)(3564.5,5115.386761363637)(3652.5,5261.080522727272)(3740.5,5407.658522727273)(3828.5,5555.073136363637)(3916.5,5703.36828409091)(4004.5,5852.564125)(4092.5,6002.664488636363)(4180.5,6153.749011363637)(4268.5,6305.792931818181)(4356.5,6458.7932045454545)(4444.5,6612.791284090909)(4532.5,6767.785272727272)(4620.5,6923.865602272727)(4708.5,7081.039670454546)(4796.5,7239.417079545454)(4884.5,7399.086931818181)(4972.5,7560.03825)(5060.5,7722.204431818182)(5148.5,7885.649727272727)(5236.5,8050.295590909091)(5324.5,8216.39771590909)(5412.5,8384.032886363637)(5500.5,8553.316522727273)(5588.5,8724.139943181819)(5676.5,8896.458170454545)(5764.5,9070.357636363637)(5852.5,9245.943272727274)(5940.5,9423.107818181817)(6028.5,9602.053295454545)(6116.5,9782.941011363637)(6204.5,9965.751875)(6292.5,10150.460022727273)(6380.5,10337.203965909091)(6468.5,10525.924090909091)(6556.5,10717.150215909092)(6644.5,10910.920056818182)(6732.5,11107.200715909092)(6820.5,11306.398920454545)(6908.5,11508.439136363637)(6996.5,11713.935943181817)(7084.5,11923.624)(7172.5,12136.768875)(7260.5,12353.715988636362)(7348.5,12574.161954545456)(7436.5,12798.799136363637)(7524.5,13029.105806818181)(7612.5,13264.319659090908)(7700.5,13505.580909090908)(7788.5,13753.832738636364)(7876.5,14009.777022727274)(7964.5,14275.649375)(8052.5,14554.259579545454)(8140.5,14849.837511363638)(8228.5,15168.880022727273)(8316.5,15522.201875)(8404.5,15935.410215909093)(8492.5,16507.840431818182)(8580.5,17813.824431818182)(8631,19480.083)(8639,19878.963)};
\addlegendentry{OstrichCEA}

\addplot[name path=pathOstrich , colourOstrich, line width=1.5pt, dashdotted] coordinates {(1,0.966)(45,51.629651685393256)(134,158.67904494382023)(223,269.89732584269666)(312,383.6197528089888)(401,499.6783033707865)(490,617.7793258426966)(579,737.6599775280899)(668,858.9771348314606)(757,981.355786516854)(846,1104.57902247191)(935,1228.659370786517)(1024,1353.5784606741574)(1113,1479.340449438202)(1202,1605.8423483146069)(1291,1732.994393258427)(1380,1860.7982471910111)(1469,1989.2398764044942)(1558,2118.2535730337077)(1647,2247.769235955056)(1736,2377.8024382022472)(1825,2508.35204494382)(1914,2639.348359550562)(2003,2770.839404494382)(2092,2902.8377078651683)(2181,3035.319370786517)(2270,3168.2678876404493)(2359,3301.7290674157307)(2448,3435.6920898876406)(2537,3570.1292921348318)(2626,3705.1524606741573)(2715,3840.691617977528)(2804,3976.759415730337)(2893,4113.360764044944)(2982,4250.445494382023)(3071,4388.062044943821)(3160,4526.229382022472)(3249,4664.950314606742)(3338,4804.172505617978)(3427,4943.860483146068)(3516,5084.05806741573)(3605,5224.723202247191)(3694,5365.906865168539)(3783,5507.576955056179)(3872,5649.704640449439)(3961,5792.306471910112)(4050,5935.380764044944)(4139,6078.9809550561795)(4228,6223.057966292135)(4317,6367.639449438202)(4406,6512.755247191011)(4495,6658.350494382023)(4584,6804.486224719101)(4673,6951.171146067415)(4762,7098.355382022472)(4851,7246.019595505618)(4940,7394.190629213483)(5029,7542.908370786517)(5118,7692.217370786517)(5207,7842.0449101123595)(5296,7992.411258426966)(5385,8143.2914269662915)(5474,8294.690213483147)(5563,8446.689786516854)(5652,8599.329584269663)(5741,8752.537707865169)(5830,8906.401494382022)(5919,9060.95129213483)(6008,9216.186011235954)(6097,9372.039516853933)(6186,9528.586505617977)(6275,9685.89011235955)(6364,9843.871674157303)(6453,10002.450629213485)(6542,10161.815808988766)(6631,10321.953292134831)(6720,10482.887561797754)(6809,10644.69070786517)(6898,10807.32670786517)(6987,10970.82293258427)(7076,11135.298629213485)(7165,11300.878033707864)(7254,11467.537505617978)(7343,11635.502033707864)(7432,11804.723314606741)(7521,11975.318898876405)(7610,12147.362651685393)(7699,12320.866617977528)(7788,12495.943325842698)(7877,12672.84586516854)(7966,12851.813775280898)(8055,13033.299011235955)(8144,13217.471460674158)(8233,13405.040426966292)(8322,13597.334921348314)(8411,13797.202966292136)(8500,14006.997168539327)(8589,14242.676)(8663.5,14719.4016)(8695,15616.104)};
\addlegendentry{Ostrich}

\addplot[name path=pathZ3str3 , colourZ3str3, line width=1.5pt, dashed, dash pattern=on 8pt off 2pt] coordinates {(1,0.011)(28,0.34405454545454545)(83,1.004)(138,1.664)(193,2.324)(248,2.984)(303,3.6490181818181817)(358,4.355)(413,5.07)(468,5.785)(523,6.5)(578,7.215)(633,7.93)(688,8.645)(743,9.36)(798,10.075)(853,10.79)(908,11.505)(963,12.22)(1018,12.935)(1073,13.65)(1128,14.365)(1183,15.08)(1238,15.795)(1293,16.51)(1348,17.234018181818183)(1403,17.999)(1458,18.769)(1513,19.541781818181818)(1568,20.355)(1623,21.217)(1678,22.11927272727273)(1733,23.054)(1788,24.01127272727273)(1843,25.001)(1898,25.992654545454545)(1953,27.022)(2008,28.067)(2063,29.112)(2118,30.1666)(2173,31.262)(2228,32.362)(2283,33.462)(2338,34.564781818181814)(2393,35.707)(2448,36.862)(2503,38.017)(2558,39.172)(2613,40.35205454545454)(2668,41.562)(2723,42.772)(2778,43.99618181818182)(2833,45.259)(2888,46.524)(2943,47.80865454545455)(2998,49.128)(3053,50.47210909090909)(3108,51.8482)(3163,53.26290909090909)(3218,54.7376)(3273,56.27590909090909)(3328,57.87347272727273)(3383,59.548418181818185)(3438,61.30281818181818)(3493,63.13972727272727)(3548,65.0678909090909)(3603,67.10025454545455)(3658,69.2492)(3713,71.49483636363637)(3768,73.84325454545454)(3823,76.31507272727272)(3878,78.93901818181818)(3933,81.7334909090909)(3988,84.68719999999999)(4043,87.8238)(4098,91.12774545454545)(4153,94.64658181818182)(4208,98.41867272727274)(4263,102.46365454545455)(4318,106.77592727272727)(4373,111.44936363636363)(4428,116.65296363636364)(4483,122.39274545454545)(4538,128.6556)(4593,135.70430909090908)(4648,143.72623636363636)(4703,152.72258181818182)(4758,162.99996363636362)(4813,175.10872727272726)(4868,189.50578181818182)(4923,208.60178181818182)(4978,241.16914545454546)(5033,301.7078909090909)(5088,407.2800363636364)(5143,527.1198909090908)(5198,654.8019272727272)(5253,840.1544181818182)(5308,1365.6359454545457)(5363,2537.6238)(5400.5,4036.3596000000002)(5412,4631.644)};
\addlegendentry{Z3str3}

\addplot[name path=pathZ3seq , colourZ3seq, line width=1.5pt, dashed, dash pattern=on 1.5pt off 2pt] coordinates {(1,0.012)(44,0.5610344827586207)(131,1.688)(218,2.819)(305,3.95)(392,5.081)(479,6.212)(566,7.343)(653,8.474)(740,9.605)(827,10.736)(914,11.867)(1001,13.03806896551724)(1088,14.256)(1175,15.474)(1262,16.692)(1349,17.91)(1436,19.128)(1523,20.360655172413793)(1610,21.658)(1697,22.963)(1784,24.28096551724138)(1871,25.664)(1958,27.056)(2045,28.463241379310343)(2132,29.935)(2219,31.414)(2306,32.8931724137931)(2393,34.421)(2480,35.987)(2567,37.553)(2654,39.13308045977011)(2741,40.778)(2828,42.431)(2915,44.084)(3002,45.78)(3089,47.52)(3176,49.26)(3263,51.02618390804598)(3350,52.851)(3437,54.678)(3524,56.54132183908046)(3611,58.455)(3698,60.38365517241379)(3785,62.377)(3872,64.40044827586208)(3959,66.485)(4046,68.61403448275863)(4133,70.79366666666667)(4220,73.036)(4307,75.34001149425288)(4394,77.72368965517242)(4481,80.208)(4568,82.774)(4655,85.4200459770115)(4742,88.19042528735632)(4829,91.09298850574713)(4916,94.14202298850574)(5003,97.34010344827585)(5090,100.71949425287357)(5177,104.2736551724138)(5264,108.0643908045977)(5351,112.12058620689655)(5438,116.49328735632184)(5525,121.25075862068965)(5612,126.37032183908046)(5699,131.87488505747126)(5786,137.83209195402299)(5873,144.3935747126437)(5960,151.6332528735632)(6047,159.56349425287357)(6134,168.32394252873564)(6221,178.00933333333333)(6308,188.61080459770116)(6395,200.22363218390805)(6482,213.0765632183908)(6569,227.277816091954)(6656,243.0501379310345)(6743,260.7920344827586)(6830,280.4905517241379)(6917,302.7097586206897)(7004,327.5999540229885)(7091,355.8960229885057)(7178,388.3605862068966)(7265,425.57027586206897)(7352,467.78589655172414)(7439,515.8811034482759)(7526,572.8783908045978)(7613,640.500264367816)(7700,721.5446551724137)(7787,819.6228965517241)(7874,943.8886896551724)(7961,1102.410471264368)(8048,1306.6646551724136)(8135,1592.898448275862)(8222,2000.9801264367816)(8309,2632.139011494253)(8396,3684.789195402299)(8483,5632.933747126437)(8528.5,7474.12825)(8532,7620.921)};
\addlegendentry{Z3seq}

\addplot[name path=pathZ3str3RE , colourZ3str3RE, line width=1.5pt, dashed, dash pattern=on 2pt off 4pt] coordinates {(1,0.004)(45,0.1892247191011236)(134,0.615)(223,1.06)(312,1.505)(401,1.95)(490,2.395)(579,2.84)(668,3.285)(757,3.73)(846,4.175)(935,4.62)(1024,5.071303370786517)(1113,5.588)(1202,6.122)(1291,6.656)(1380,7.209224719101123)(1469,7.827)(1558,8.45)(1647,9.073)(1736,9.696)(1825,10.319)(1914,10.942)(2003,11.565)(2092,12.188)(2181,12.834370786516855)(2270,13.543)(2359,14.255)(2448,14.967)(2537,15.679)(2626,16.391)(2715,17.103)(2804,17.815)(2893,18.527)(2982,19.239)(3071,19.951)(3160,20.663)(3249,21.381685393258426)(3338,22.166)(3427,22.967)(3516,23.768)(3605,24.569)(3694,25.37)(3783,26.171)(3872,26.972)(3961,27.773)(4050,28.574)(4139,29.375)(4228,30.181932584269664)(4317,31.054)(4406,31.944)(4495,32.834)(4584,33.724)(4673,34.614)(4762,35.504)(4851,36.394)(4940,37.29030337078652)(5029,38.252)(5118,39.231)(5207,40.21)(5296,41.189)(5385,42.1703595505618)(5474,43.212)(5563,44.28)(5652,45.348)(5741,46.41661797752809)(5830,47.539)(5919,48.696)(6008,49.853)(6097,51.045505617977526)(6186,52.291)(6275,53.542932584269664)(6364,54.86)(6453,56.19924719101124)(6542,57.602)(6631,59.045887640449436)(6720,60.55431460674157)(6809,62.11923595505618)(6898,63.772)(6987,65.50240449438202)(7076,67.33822471910112)(7165,69.29493258426966)(7254,71.38649438202248)(7343,73.63291011235955)(7432,76.06348314606741)(7521,78.76337078651686)(7610,81.7866179775281)(7699,85.20116853932583)(7788,89.14226966292135)(7877,93.84008988764046)(7966,99.66762921348314)(8055,106.92501123595505)(8144,116.53524719101124)(8233,130.10767415730336)(8322,150.67694382022472)(8411,185.7845842696629)(8500,252.37134831460673)(8589,453.2947752808989)(8655.5,1213.1201363636364)(8679,2048.545)};
\addlegendentry{Z3str3RE}
